%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.9]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{2cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Hossein} % Your first name
\familyname{Razizadeh} % Your last name

% All information in this block is optional, comment out any lines you don't need
%\title{Curriculum Vitae}

\address{11840 Sealord Rd, Richmond BC, Canada}{}
% \address{Tehran, Iran}{}
% \address{Istanbul, Turkey}{}
%{Postal code: 1495846654}
\mobile{(+1) 604 346 8334}
% \mobile{(+98) 9352227135}
% \mobile{(+90) 554 354 7025}

\email{sm.hosein@gmail.com}
\homepage{www.linkedin.com/in/hossein-razizadeh-76549613a}{} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------
%\usepackage{xpatch}
%\xpatchcmd{\makecvhead}{\\[2.5em]}{\\}{}{}

\begin{document}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage
%
%\recipient{}{} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vitae{}} % List of enclosed documents
%
%\makelettertitle % Print letter title
%
%%I am critical problem solver with solid knowledge in algorithm.
%\lipsum[1-2] % Dummy text
%\lipsum[4] % Dummy text
%
%\makeletterclosing % Print letter signature
%
%\newpage

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------
\vspace*{-0.3cm}

\makecvtitle % Print the CV title
\vspace*{-1cm}


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------
\section{Summary}

\cvitem{}{Software Engineer with \textbf{over ten years of experience} in designing and developing high-performance software systems across various sectors. Expert in solving complex challenges and enhancing software efficiency through \textbf{advanced algorithms} and \textbf{parallel processing} techniques. Demonstrated track record of excellence, highlighted by prestigious awards in \textbf{programming competitions such as RoboCup and ICPC}.
}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\cventry{2022--2024}{Senior Software Engineer}{\textsc{OVOU}}{Vancouver}{Canada}{ 
\begin{itemize}
\item \textbf{Back Office System Design and Implementation:} Led the design and implementation of a comprehensive back-office system within Zoho tailored for the fulfillment team. This initiative quadrupled operational efficiency, enhancing workflows and productivity by making processes \textbf{4x faster}.
\item \textbf{Backend Development:} Worked on the backend team using Django to develop and maintain APIs. Responsibilities included refactoring existing code, implementing new API functionalities, and managing data migrations to improve data handling and system stability.
\end{itemize}
}
%\subsection{Vocational}
%\cventry{2021--Current}{Freelance Software Engineer}{\textsc{}}{Tehran, Iran}{}{}

\cventry{2016--2021}{Senior Software Engineer}{\textsc{Cafe Bazaar}}{Tehran}{Iran}{ 
\begin{itemize}
\item \textbf{Computer Vision Service Development:} Collaborated with data scientists to develop and maintain machine learning models for computer vision services, including a high-efficiency watermark detection system capable of processing 60 images per second. Played a pivotal role in the backend development, enhancing service performance.
\item \textbf{Accuracy in POI Extraction:} Achieved a \textbf{98.5\% accuracy} rate in extracting Points of Interest (POI) from images captured by street-imaging cars, utilizing a combination of automated models and human annotations.
\item \textbf{Street Imaging Project Management:}  Led the "Street Imaging" project, developed a Windows application to handle image capture at 30 fps from three cameras on moving vehicles, and managed the acquisition and processing of over \textbf{200 million high-quality street images} to enhance the "Balad" map's POI database.
\end{itemize}
}

%------------------------------------------------

\cventry{2014--2016}{Senior Software Engineer}{\textsc{Sabz Biomedicals}}{Tehran, Iran}{}{Developed high-performance software for karyotyping and 2D gel image analysis, significantly enhancing diagnostic capabilities in medical laboratories. This advanced toolset streamlined data processing, improved accuracy in genetic analysis, and supported critical research and clinical decisions.
}

\cventry{2007--2008}{Software Engineer}{\textsc{Pooya Fanavaran Kosar}}{Tehran, Iran}{}{Engineered a high-performance mobile in-car speed camera system using C++, significantly boosting speed detection accuracy and system reliability. This innovation was recognized with the \textbf{first-place award in the Applied Research category at the Young Khwarizmi Festival}.
}

\cventry{2005}{Software Engineering Internship}{\textsc{Rabi Kosar}}{Tehran, Iran}{}{Developed specialized code in C and Embedded-C to facilitate lossless high-speed signal transmission from DSP boards to PCs, enhancing data integrity and processing efficiency.
}

\cventry{2003--2016}{Computer Group Manager and Lecturer}{\textsc{Allameh Helli High School}}{Tehran, Iran}{}{Managed a team of 10 computer science teachers and taught courses in programming, algorithms and data structures.
}

%\cventry{2005}{Software Engineering Internship}{\textsc{Rabi Kosar}}{Tehran}{}{Programming on sundance dsp boards}


%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards and Honors}

\cventry{2005}{World Championship Award}{\textit{RoboCup 2005}}{Osaka, Japan}{}{
1st place among 32 international teams in 3D Soccer Simulation league}
\cventry{2007, 2006, 2005}{5th, 6th, 6th Team Rank}{\textit{ACM ICPC West Asia Region Regional Contest}}{Tehran, Iran}{}{}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}

\cventry{2013--2016}{MSc in Computer Science}{The University of Tehran}{Tehran}{Iran}{Thesis: Development and Implementation of an Image to Speech System to be used in Persian language.}

\cventry{2003--2009}{BSc in Computer Engineering}{Amirkabir University of Technology, Tehran Polytechnic}{Tehran}{Iran}{Thesis: Evaluation of reinforcement learning algorithms on control problems with delayed reward signals.}
%\cventry{1999-2003}{Diploma in Mathematics and Physics}{Allameh Helli Highschool}{Tehran}{Iran}{Allameh Helli is the Tehran branch of NODET(National Organization for Development of Exceptional Talents).}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

%\section{Languages}
%
%\cvitemwithcomment{}{
%\begin{tabular}{p{3cm} p{3cm} p{3cm}}
%English & Persian & Azerbaijani
%\end{tabular}
%}{}

%\cvitemwithcomment{Persian}{Mother Tongue}{}
%\cvitemwithcomment{Azerbaijani}{Mother Tongue}{}
%\cvitemwithcomment{English}{Professional working proficiency}{}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Skills}

\cvitem{Computer Skills}{
	Programming Languages: \textbf{C++, C, Python} \newline
	Technologies: \textbf{Linux, Docker, Kubernetes, gRPC, OpenCV, Git, Django}
}
	
\cvitem{Analytical Skills}{\textbf{Data Structure, Design and Analysis of Algorithms, Parallel Processing, Design Patterns, System Design, Artificial Neural Networks, Genetic Algorithm, Image Processing}}


\end{document}